---
title: "Process Sim 3"
format: html
---
```{r}
library(tidyverse)
library(ggdist)
library(ggthemes)
library(tidyquant)
```


```{r}
load("../data/Sim_3.RData")

anyNA(Sim_3)
df_with_na <- Sim_3[apply(is.na(Sim_3), 1, any), ]
```

```{r}
# "impute" all NaN with 1 because:
cumprod(c(1,0,1)) / (cumprod(c(1,0,1)) + cumprod(c(1-1,1-0,1-1)))

cumprod(c(1,0.0000001,1)) / (cumprod(c(1,0.0000001,1)) + cumprod(c(1-1,1-0.0000001,1-1)))

# correct?
Sim_3$BESc <- ifelse(is.nan(Sim_3$BESc), 1, Sim_3$BESc)
```

```{r}
df_with_inf <- Sim_3 %>%
  filter(if_any(where(is.numeric), ~ !is.finite(.)))
```

```{r}
df_with_nan <- Sim_3 %>%
  filter(if_any(where(is.numeric), ~ is.nan(.)))
```

missingness: when testing against the Hu and get inf evd 

IF missing -> PMP 0.5 because informative and complement are both infinitely bad

```{r}
Sim_3$n_sample <- Sim_3$n_sample*3

# Add indicator or partial
Sim_3$ind_p_all <- ifelse(Sim_3$ind_p1 == 1 & Sim_3$ind_p2 == 1 & Sim_3$ind_p3 == 1, 1, 0)
```


```{r}
Sim_3 <- Sim_3 %>%
  group_by(n_sample, d, c) %>%
  mutate(
    MAPDu = abs((PMP1u_H - BESu) / PMP1u_H) * 100, # mean average percentage difference
    MSDu = PMP1u_H - BESu, # mean signed difference
    MAPDc = abs((PMP1c_H - BESc) / PMP1c_H) * 100, # mean average percentage difference
    MSDc = PMP1c_H - BESc # mean signed difference
  )
```

Aggregated dataset
```{r}
Sim_3_agg <- Sim_3 %>%
  group_by(n_sample, c, d) %>%
  summarise(PMP1u_H = mean(PMP1u_H),
            PMP1c_H = mean(PMP1c_H),
            BESc = mean(BESc),
            BESu = mean(BESu),
            MAPDu = mean(MAPDu),
            MAPDc = mean(MAPDc),
            MSDu = mean(MSDu),
            MSDc = mean(MSDc))
```

```{r}
Sim_3$MAPDu[is.na.data.frame(Sim_3$MAPDu)] <- 0
max_mapdu <- max(Sim_3$MAPDu[is.finite(Sim_3$MAPDu)])
Sim_3$MAPDu[is.infinite(Sim_3$MAPDu)] <- max_mapdu

Sim_3$MAPDc[is.na.data.frame(Sim_3$MAPDc)] <- 0
max_mapdc <- max(Sim_3$MAPDc[is.finite(Sim_3$MAPDc)])
Sim_3$MAPDc[is.infinite(Sim_3$MAPDc)] <- max_mapdc

Sim_3_agg_2 <- Sim_3 %>%
  group_by(n_sample, c, d) %>%
  summarise(PMP1u_H = mean(PMP1u_H),
            PMP1c_H = mean(PMP1c_H),
            BESc = mean(BESc),
            BESu = mean(BESu),
            MAPDu = mean(MAPDu),
            MAPDc = mean(MAPDc),
            MSDu = mean(MSDu),
            MSDc = mean(MSDc))


```

```{r}
#check the outlier
test <- Sim_3 %>% filter(n_sample == 1500 & c == 0.8 & d == 0.8)
```

# Plot

## Lineplot MAPD: Bayes Factor tested against the unconstrained Hypothesis
```{r}
Sim_3_agg_2 %>% filter(d != 0) %>% ggplot() +
  geom_line(aes(
    x = as.factor(n_sample),
    y = MAPDu,
    color = as.factor(d),
    group = 1
  )) +
  labs(x = "Sample Size (Total)", y = "MAPD") +
  ggtitle("MAPD: Tested against unconstrained Hypothesis") +
  scale_color_discrete(guide = "none") +
  theme_bw() +
  facet_grid(c ~ d) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Mean Average Percentage Difference for effect size d from 0.2 to 0.8 and correlation of 0.0 to 0.8. Bayesfactor tested against the unconstrained hypothesis.

## Lineplot MAPD: Bayes Factor tested against the complement Hypothesis
```{r}
Sim_3_agg_2 %>% filter(d != 0) %>% ggplot() +
  geom_line(aes(
    x = as.factor(n_sample),
    y = MAPDc,
    color = as.factor(d),
    group = 1
  )) +
  labs(x = "Sample Size (Total)", y = "MAPD") +
  ggtitle("MAPD: Tested against complement Hypothesis") +
  scale_color_discrete(guide = "none") +
  theme_bw() +
  facet_grid(c ~ d) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Lineplot MSD: Bayes Factor tested against the unconstrained Hypothesis
```{r}
Sim_3_agg %>% filter(d != 0) %>% ggplot() +
  geom_line(aes(
    x = as.factor(n_sample),
    y = MSDu,
    color = as.factor(d),
    group = 1
  )) +
  labs(x = "Sample Size (Total)", y = "MSD") +
  ggtitle("MSD: Tested against unconstrained Hypothesis") +
  scale_color_discrete(guide = "none") +
  theme_bw() +
  facet_grid(c ~ d) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Lineplot MSD: Bayes Factor tested against the complement Hypothesis
```{r}
Sim_3_agg %>% filter(d != 0) %>% ggplot() +
  geom_line(aes(
    x = as.factor(n_sample),
    y = MSDc,
    color = as.factor(d),
    group = 1
  )) +
  labs(x = "Sample Size (Total)", y = "MSD") +
  ggtitle("MSD: Tested against complement Hypothesis") +
  scale_color_discrete(guide = "none") +
  theme_bw() +
  facet_grid(c ~ d) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


