---
title: "Plots Error"
format: html
---
```{r}
library(tidyverse)
library(ggdist)
library(ggthemes)
library(tidyquant)
```


```{r}
load("../data/Sim_1.RData")

anyNA(Sim_1)
df_with_na <- Sim_1[apply(is.na(Sim_1), 1, any), ]
# only NA in BESc, bc of 0 in one of the PMPs

# "impute" all NaN with 1 because:
cumprod(c(0.6,0,1)) / (cumprod(c(0.6,0,1)) + cumprod(c(1-0.6,1-0,1-1)))

cumprod(c(0.6,0.0000001,1)) / (cumprod(c(0.6,0.0000001,1)) + cumprod(c(1-0.6,1-0.0000001,1-1)))

# correct?
Sim_1$BESc <- ifelse(is.nan(Sim_1$BESc), 1, Sim_1$BESc)
```

```{r}

```


```{r}
Sim_1$n_sample <- Sim_1$n_sample*3

# Add indicator or partial
Sim_1$ind_p_all <- ifelse(Sim_1$ind_p1 == 1 & Sim_1$ind_p2 == 1 & Sim_1$ind_p3 == 1, 1, 0)
```


```{r}
Sim_1 <- Sim_1 %>%
  group_by(n_sample, d, c) %>%
  mutate(
    MAPDu = abs((PMP1u_H - BESu) / PMP1u_H) * 100, # mean average percentage difference
    MSDu = PMP1u_H - BESu, # mean signed difference
    MAPDc = abs((PMP1c_H - BESc) / PMP1c_H) * 100, # mean average percentage difference
    MSDc = PMP1c_H - BESc # mean signed difference
  )

# Set NaNs in MAPDc to 0 bc they only accured if abs((PMP1c_H - BESc) / PMP1c_H) = abs((0 - 0) / 0)
Sim_1$MAPDc <- ifelse(is.nan(Sim_1$MAPDc), 0, Sim_1$MAPDc)

# Important note: all d = 0 end in Inf for MAPDc (as expected)
```

Aggregated dataset
```{r}
Sim_1_agg <- Sim_1 %>%
  group_by(n_sample, c, d) %>%
  summarise(PMP1u_H = mean(PMP1u_H),
            PMP1c_H = mean(PMP1c_H),
            BESc = mean(BESc),
            BESu = mean(BESu),
            MAPDu = mean(MAPDu),
            MAPDc = mean(MAPDc),
            MSDu = mean(MSDu),
            MSDc = mean(MSDc))
```

# Plot

## Lineplot MAPD: Bayes Factor tested against the unconstrained Hypothesis
```{r}
Sim_1_agg %>% filter(d != 0) %>% ggplot() +
  geom_line(aes(
    x = as.factor(n_sample),
    y = MAPDu,
    color = as.factor(d),
    group = 1
  )) +
  labs(x = "Sample Size (Total)", y = "MAPD") +
  ggtitle("MAPD: Tested against unconstrained Hypothesis") +
  scale_color_discrete(guide = "none") +
  theme_bw() +
  facet_grid(c ~ d) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Mean Average Percentage Difference for effect size d from 0.2 to 0.8 and correlation of 0.0 to 0.8. Bayesfactor tested against the unconstrained hypothesis.

## Lineplot MAPD: Bayes Factor tested against the complement Hypothesis
```{r}
Sim_1_agg %>% filter(d != 0) %>% ggplot() +
  geom_line(aes(
    x = as.factor(n_sample),
    y = MAPDc,
    color = as.factor(d),
    group = 1
  )) +
  labs(x = "Sample Size (Total)", y = "MAPD") +
  ggtitle("MAPD: Tested against complement Hypothesis") +
  scale_color_discrete(guide = "none") +
  theme_bw() +
  facet_grid(c ~ d) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```




# Descriptive stats
```{r}
Sim_1_agg
```




## Lineplot MSD: Bayes Factor tested against the unconstrained Hypothesis
```{r}
Sim_1_agg %>% filter(d != 0) %>% ggplot() +
  geom_line(aes(
    x = as.factor(n_sample),
    y = MSDu,
    color = as.factor(d),
    group = 1
  )) +
  labs(x = "Sample Size (Total)", y = "MSD") +
  ggtitle("MSD: Tested against unconstrained Hypothesis") +
  scale_color_discrete(guide = "none") +
  theme_bw() +
  facet_grid(c ~ d) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Lineplot MSD: Bayes Factor tested against the complement Hypothesis
```{r}
Sim_1_agg %>% filter(d != 0) %>% ggplot() +
  geom_line(aes(
    x = as.factor(n_sample),
    y = MSDc,
    color = as.factor(d),
    group = 1
  )) +
  labs(x = "Sample Size (Total)", y = "MSD") +
  ggtitle("MSD: Tested against complement Hypothesis") +
  scale_color_discrete(guide = "none") +
  theme_bw() +
  facet_grid(c ~ d) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```




















# Complement
```{r}
Sim_1 %>% 
  filter(n_sample %in% c(75, 150, 300, 1500) & c == 0.2 & d == 0.2) %>%
  ggplot(aes(y = factor(n_sample), x = BESc, fill = factor(ind_comp))) +
  
  geom_boxplot(
    width = 0.12,
    # removing outliers
    outlier.color = NA,
    alpha = 0.5
  ) +
  
  stat_dots(
    # ploting on left side
    side = "right",
    # adjusting position
    justification = 1.2,
    # adjust grouping (binning) of observations
    #binwidth = 0.25
    alpha = 0.2
  ) +
  
  # Themes and Labels
  scale_fill_tq() +
  theme_tq() +
  labs(
    title = "Complete Hypothesis: PMPs against complement",
    x = "PMP1c",
    y = "",
    fill = "Indicator"
  ) +
  
  facet_wrap(~ n_sample, scales = "free") +
  theme(
    axis.ticks.y = element_blank(), 
    axis.text.y = element_blank())
```
```{r}
Sim_1 %>% 
  filter(n_sample %in% c(75, 150, 300, 1500) & c == 0.2 & d == 0.2) %>%
  ggplot(aes(y = factor(n_sample), x = PMP1c_H, fill = factor(ind_p_all))) +
  
  geom_boxplot(
    width = 0.12,
    # removing outliers
    outlier.color = NA,
    alpha = 0.5
  ) +
  
  stat_dots(
    # ploting on left side
    side = "right",
    # adjusting position
    justification = 1.2,
    # adjust grouping (binning) of observations
    #binwidth = 0.25
    alpha = 0.2
  ) +
  
  # Themes and Labels
  scale_fill_tq() +
  theme_tq() +
  labs(
    title = "Complete Hypothesis: PMPs against complement",
    x = "PMP1c",
    y = "",
    fill = "Indicator"
  ) +
  
  facet_wrap(~ n_sample, scales = "free") +
  theme(
    axis.ticks.y = element_blank(), 
    axis.text.y = element_blank())
```



# Unconstrained
```{r}
Sim_1 %>% 
  filter(n_sample %in% c(75, 150, 300, 1500) & c == 0.2 & d == 0.2) %>%
  ggplot(aes(y = factor(n_sample), x = BESu, fill = factor(ind_comp))) +
  
  geom_boxplot(
    width = 0.12,
    # removing outliers
    outlier.color = NA,
    alpha = 0.5
  ) +
  
  stat_dots(
    # ploting on left side
    side = "right",
    # adjusting position
    justification = 1.2,
    # adjust grouping (binning) of observations
    #binwidth = 0.25
    alpha = 0.2
  ) +
  
  # Themes and Labels
  scale_fill_tq() +
  theme_tq() +
  labs(
    title = "Complete Hypothesis: PMPs against complement",
    x = "PMP1c",
    y = "",
    fill = "Indicator"
  ) +
  
  facet_wrap(~ n_sample, scales = "free") +
  theme(
    axis.ticks.y = element_blank(), 
    axis.text.y = element_blank())
```

```{r}
Sim_1 %>% 
  filter(n_sample %in% c(75, 150, 300, 1500) & c == 0.2 & d == 0.2) %>%
  ggplot(aes(y = factor(n_sample), x = PMP1u_H, fill = factor(ind_p_all))) +
  
  geom_boxplot(
    width = 0.12,
    # removing outliers
    outlier.color = NA,
    alpha = 0.5
  ) +
  
  stat_dots(
    # ploting on left side
    side = "right",
    # adjusting position
    justification = 1.2,
    # adjust grouping (binning) of observations
    #binwidth = 0.25
    alpha = 0.2
  ) +
  
  # Themes and Labels
  scale_fill_tq() +
  theme_tq() +
  labs(
    title = "Complete Hypothesis: PMPs against complement",
    x = "PMP1c",
    y = "",
    fill = "Indicator"
  ) +
  
  facet_wrap(~ n_sample, scales = "free") +
  theme(
    axis.ticks.y = element_blank(), 
    axis.text.y = element_blank())
```

