---
title: "Simulateion 1&2"
format: html
---

Start Timer
```{r}
t1 <- Sys.time()
```


```{r}
library(MASS)
library(tidyverse)
library(BFpack)
source("../scripts/function.R")
```

# Global Parameters
```{r}
# seed
set.seed(1337)

# number of simulations
nsim <- 500

# sample and effect sizes
n_sample <- c(25, 75, 50, 150, 100, 300, 500, 1500)
d <- c(0, 0.2, 0.5, 0.8)
c <- c(0, 0.2, 0.5, 0.8)
```

# Simulation 1&2
Define Hypotheses
```{r}
h_p1 <- "mu_1 > mu_2"
h_p2 <- "mu_2 > mu_3"
h_p3 <- "mu_3 > mu_4"
H <- "mu_1 > mu_2 > mu_3 > mu_4"
```

## Simulation 1

### Simulation 1 Study 1
Simulates one dataset in which we test H_complete against BES, calculated from the same dataset.
```{r}
Sim_1_Study_1 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Complete Hypothesis
      BF_H = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = H
        )
      ),
      BF1u_H = BF_H$BFtu_confirmatory[[1]],
      PMP1c_H = BF_H$PHP_confirmatory[[1]],
      PMP1u_H = BF1u_H / (BF1u_H + 1),
      # BF Partial Study 1
      BF_h_p1 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p1
        )
      ),
      BF1u_h_p1 = BF_h_p1$BFtu_confirmatory[[1]],
      PMP1c_h_p1 = BF_h_p1$PHP_confirmatory[[1]],
      PMP1u_h_p1 = BF1u_h_p1 / (BF1u_h_p1 + 1),
      # BF Partial Study 2
      BF_h_p2 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p2
        )
      ),
      BF1u_h_p2 = BF_h_p2$BFtu_confirmatory[[1]],
      PMP1c_h_p2 = BF_h_p2$PHP_confirmatory[[1]],
      PMP1u_h_p2 = BF1u_h_p2 / (BF1u_h_p2 + 1),
      # BF Partial Study 3
      BF_h_p3 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p3
        )
      ),
      BF1u_h_p3 = BF_h_p3$BFtu_confirmatory[[1]],
      PMP1c_h_p3 = BF_h_p3$PHP_confirmatory[[1]],
      PMP1u_h_p3 = BF1u_h_p3 / (BF1u_h_p3 + 1)
    ) %>%
    rowwise() %>%
    mutate(BESc = prod(c(PMP1c_h_p1, PMP1c_h_p2, PMP1c_h_p3)) / (prod(c(
      PMP1c_h_p1, PMP1c_h_p2, PMP1c_h_p3
    )) + prod(
      c(1 - PMP1c_h_p1, 1 - PMP1c_h_p2, 1 - PMP1c_h_p3)
    )),
    BESu = prod(c(PMP1u_h_p1, PMP1u_h_p2, PMP1u_h_p3)) / (prod(c(
      PMP1u_h_p1, PMP1u_h_p2, PMP1u_h_p3
    )) + prod(
      c(1 - PMP1u_h_p1, 1 - PMP1u_h_p2, 1 - PMP1u_h_p3)
    ))) 
```

indicate if complete and partial hypotheses are true
```{r}
Sim_1_Study_1 <- addIndicator(Sim_1_Study_1)
```

Safe Data
```{r}
save(Sim_1_Study_1, file = "../data/Sim_1_Study_1.RData")
```

Timer
```{r}
Sys.time() - t1
```

Clean Workspace
```{r}
rm(Sim_1_Study_1)
```


## Simulation 2

### Simulation 2 Study 1: Complete Hypothesis
```{r}
Sim_2_Study_1 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Complete Hypothesis
      BF_H = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = H
        )
      ),
      BF1u_H = BF_H$BFtu_confirmatory[[1]],
      PMP1c_H = BF_H$PHP_confirmatory[[1]],
      PMP1u_H = BF1u_H / (BF1u_H + 1))
```

indicate if complete and partial hypotheses are true
```{r}
Sim_2_Study_1 <- addIndicator(Sim_2_Study_1)
```

Safe Data
```{r}
save(Sim_2_Study_1, file = "../data/Sim_2_Study_1.RData")
```

Timer
```{r}
Sys.time() - t1
```

Clean Workspace
```{r}
rm(Sim_2_Study_1)
```

### Simulation 2 Study 2: mu_1 > mu_2
```{r}
Sim_2_Study_2 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Partial Study 1
      BF_h_p1 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p1
        )
      ),
      BF1u_h_p1 = BF_h_p1$BFtu_confirmatory[[1]],
      PMP1c_h_p1 = BF_h_p1$PHP_confirmatory[[1]],
      PMP1u_h_p1 = BF1u_h_p1 / (BF1u_h_p1 + 1)
    )
```

indicate if complete and partial hypotheses are true
```{r}
Sim_2_Study_2 <- addIndicator(Sim_2_Study_2)
```

Safe Data
```{r}
save(Sim_2_Study_2, file = "../data/Sim_2_Study_2.RData")
```

Timer
```{r}
Sys.time() - t1
```

Clean Workspace
```{r}
rm(Sim_2_Study_2)
```

### Simulation 2 Study 3: mu_2 > mu_3
```{r}
Sim_2_Study_3 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Partial Study 2
      BF_h_p2 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p2
        )
      ),
      BF1u_h_p2 = BF_h_p2$BFtu_confirmatory[[1]],
      PMP1c_h_p2 = BF_h_p2$PHP_confirmatory[[1]],
      PMP1u_h_p2 = BF1u_h_p2 / (BF1u_h_p2 + 1)
    )
```

indicate if complete and partial hypotheses are true
```{r}
Sim_2_Study_3 <- addIndicator(Sim_2_Study_3)
```

Safe Data
```{r}
save(Sim_2_Study_3, file = "../data/Sim_2_Study_3.RData")
```

Timer
```{r}
Sys.time() - t1
```

Clean Workspace
```{r}
rm(Sim_2_Study_3)
```

### Simulation 2 Study 4: mu_3 > mu_4
```{r}
Sim_2_Study_4 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Partial Study 3
      BF_h_p3 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p3
        )
      ),
      BF1u_h_p3 = BF_h_p3$BFtu_confirmatory[[1]],
      PMP1c_h_p3 = BF_h_p3$PHP_confirmatory[[1]],
      PMP1u_h_p3 = BF1u_h_p3 / (BF1u_h_p3 + 1)
    )
```

indicate if complete and partial hypotheses are true
```{r}
Sim_2_Study_4 <- addIndicator(Sim_2_Study_4)
```

Safe Data
```{r}
save(Sim_2_Study_4, file = "../data/Sim_2_Study_4.RData")
```

Timer
```{r}
Sys.time() - t1
```

Clean Workspace
```{r}
rm(Sim_2_Study_4)
```

End Timer
```{r}
Sys.time() - t1
```
