---
title: "Simulateion 1&2"
format: html
---

Start Timer
```{r}
t1 <- Sys.time()
```

```{r}
library(MASS)
library(tidyverse)
library(BFpack)
library(purrr)
source("../scripts/function.R")
```

# Global Parameters
```{r}
# seed
set.seed(1337)

# number of simulations
nsim <- 10

# sample and effect sizes
d <- c(0, 0.2, 0.5, 0.8)
c <- c(0, 0.2, 0.5, 0.8)
```

# Simulation 1&2
Define Hypotheses
```{r}
h_p1 <- "mu_1 > mu_2"
h_p2 <- "mu_2 > mu_3"
h_p3 <- "mu_3 > mu_4"
H <- "mu_1 > mu_2 > mu_3 > mu_4"
```

## Simulation 1

### Simulation 1 Study 1
```{r}
n_sample <- c(25, 50, 100, 500)
```

Simulates one dataset in which we test H_complete against BES, calculated from the same dataset.
```{r}
Sim_1_Study_1 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      BF_h_p1 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p1
        )
      ),
      BF1u_h_p1 = BF_h_p1$BFtu_confirmatory[[1]],
      PMP1c_h_p1 = BF_h_p1$PHP_confirmatory[[1]],
      PMP1u_h_p1 = BF1u_h_p1 / (BF1u_h_p1 + 1)) %>%
  addIndicator("p1")

```

### Sim_1_Study_2: Partial Hypothesis mu_2 > mu_3
```{r}
Sim_1_Study_2 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      BF_h_p2 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p2
        )
      ),
      BF1u_h_p2 = BF_h_p2$BFtu_confirmatory[[1]],
      PMP1c_h_p2 = BF_h_p2$PHP_confirmatory[[1]],
      PMP1u_h_p2 = BF1u_h_p2 / (BF1u_h_p2 + 1)) %>%
  addIndicator("p2")

```

### Sim_1_Study_3: Partial Hypothesis mu_3 > mu_4
```{r}
Sim_1_Study_3 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      BF_h_p3 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p3
        )
      ),
      BF1u_h_p3 = BF_h_p3$BFtu_confirmatory[[1]],
      PMP1c_h_p3 = BF_h_p3$PHP_confirmatory[[1]],
      PMP1u_h_p3 = BF1u_h_p3 / (BF1u_h_p3 + 1)) %>%
  addIndicator("p3")

```

### Sim_1_Study_4: Aggregate Study 1-3 for complete Dataset
```{r}
# Assuming df1, df2, df3 are your three DataFrames
#df_list <- list(Sim_1_Study_1, Sim_1_Study_2, Sim_1_Study_3)

# Compute the element-wise mean of s_mu (ensuring a vector output)
pooled_s_mu <- map2(Sim_1_Study_1$s_mu, 
                    map2(Sim_1_Study_2$s_mu, Sim_1_Study_3$s_mu, `+`), 
                    ~ (.x + .y) / 3)

# Compute the element-wise mean of s_Sigma (ensuring a matrix output)
pooled_s_Sigma <- map2(Sim_1_Study_1$s_Sigma, 
                       map2(Sim_1_Study_2$s_Sigma, Sim_1_Study_3$s_Sigma, `+`), 
                       ~ (.x + .y) / 3)

# Create a new DataFrame with the right format
Sim_1 <- Sim_1_Study_1 %>%
  select(nsim, n_sample, d, c, PMP1c_h_p1, PMP1u_h_p1, ind_p1) %>%
  left_join(Sim_1_Study_2 %>% select(nsim, n_sample, d, c, PMP1c_h_p2, PMP1u_h_p2, ind_p2), by = c("nsim", "n_sample", "d", "c")) %>%
  left_join(Sim_1_Study_3 %>% select(nsim, n_sample, d, c, PMP1c_h_p3, PMP1u_h_p3, ind_p3), by = c("nsim", "n_sample", "d", "c"))

# Remove partial DFs, as all information is contained in pooled df
rm(Sim_1_Study_1, Sim_1_Study_2, Sim_1_Study_3) 

Sim_1$s_mu <- pooled_s_mu
Sim_1$s_Sigma <- pooled_s_Sigma

Sim_1 <- Sim_1 %>%
  rowwise() %>%
   mutate(
    BF_H = list(BF(
      x = s_mu,
      Sigma = s_Sigma / (n_sample * 3), # multiply sample size by 3 to pool partial sample sizes
      n = n_sample * 3,
      hypothesis = H
    )),
    BF1u_H = BF_H$BFtu_confirmatory[[1]],
    PMP1c_H = BF_H$PHP_confirmatory[[1]],
    PMP1u_H = BF1u_H / (BF1u_H + 1)
  ) %>%
  addIndicator("comp")

```

### Clean outcome DF and compute BES
```{r}
Sim_1 <- Sim_1 %>%
  select(-c("s_mu", "s_Sigma", "BF_H", "BF1u_H")) %>%
  mutate(
    BESc = prod(PMP1c_h_p1, PMP1c_h_p2, PMP1c_h_p3) / (
      prod(PMP1c_h_p1, PMP1c_h_p2, PMP1c_h_p3) + prod(1 - PMP1c_h_p1, 1 - PMP1c_h_p2, 1 -
                                                        PMP1c_h_p3)
    ),
    BESu = prod(PMP1u_h_p1, PMP1u_h_p2, PMP1u_h_p3) / (
      prod(PMP1u_h_p1, PMP1u_h_p2, PMP1c_h_p3) + prod(1 - PMP1u_h_p1, 1 - PMP1u_h_p2, 1 -
                                                        PMP1u_h_p3)
    )
  )
```

```{r}
save(Sim_1, file = "../data/Sim_1.RData")
```


Timer
```{r}
Sys.time() - t1
```

Clean Workspace
```{r}
rm(Sim_1)
```


## Simulation 2


### Simulation 2 Study 1: Complete Hypothesis
```{r}
n_sample <- c(75, 150, 300, 1500)
```

```{r}
Sim_2_Study_1 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Complete Hypothesis
      BF_H = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = H
        )
      ),
      BF1u_H = BF_H$BFtu_confirmatory[[1]],
      PMP1c_H = BF_H$PHP_confirmatory[[1]],
      PMP1u_H = BF1u_H / (BF1u_H + 1)) %>%
  addIndicator("comp")
```

### Set Saple Size for partial Studies
```{r}
n_sample <- c(25, 50, 100, 500)
```

### Simulation 2 Study 2: mu_1 > mu_2
```{r}
Sim_2_Study_2 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Partial Study 1
      BF_h_p1 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p1
        )
      ),
      BF1u_h_p1 = BF_h_p1$BFtu_confirmatory[[1]],
      PMP1c_h_p1 = BF_h_p1$PHP_confirmatory[[1]],
      PMP1u_h_p1 = BF1u_h_p1 / (BF1u_h_p1 + 1)
    ) %>%
  addIndicator("p1")
```


### Simulation 2 Study 3: mu_2 > mu_3
```{r}
Sim_2_Study_3 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Partial Study 2
      BF_h_p2 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p2
        )
      ),
      BF1u_h_p2 = BF_h_p2$BFtu_confirmatory[[1]],
      PMP1c_h_p2 = BF_h_p2$PHP_confirmatory[[1]],
      PMP1u_h_p2 = BF1u_h_p2 / (BF1u_h_p2 + 1)
    ) %>%
  addIndicator("p2")
```


### Simulation 2 Study 4: mu_3 > mu_4
```{r}
Sim_2_Study_4 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Partial Study 3
      BF_h_p3 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p3
        )
      ),
      BF1u_h_p3 = BF_h_p3$BFtu_confirmatory[[1]],
      PMP1c_h_p3 = BF_h_p3$PHP_confirmatory[[1]],
      PMP1u_h_p3 = BF1u_h_p3 / (BF1u_h_p3 + 1)
    ) %>%
  addIndicator("p3")
```

### Process Simulation 2
```{r}
# Sample Size to match partial studies
Sim_2_Study_1$n_sample <- Sim_2_Study_1$n_sample/3
```

```{r}
Sim_2 <- Sim_2_Study_2 %>%
  select(nsim, n_sample, d, c, PMP1c_h_p1, PMP1u_h_p1, ind_p1)  %>%
  left_join(
    Sim_2_Study_3 %>% select(nsim, n_sample, d, c, PMP1c_h_p2, PMP1u_h_p2, ind_p2),
    by = c("nsim", "n_sample", "d", "c")
  ) %>%
  left_join(
    Sim_2_Study_4 %>% select(nsim, n_sample, d, c, PMP1c_h_p3, PMP1u_h_p3, ind_p3),
    by = c("nsim", "n_sample", "d", "c")
  ) %>%
  left_join(
    Sim_2_Study_1 %>% select(nsim, n_sample, d, c, PMP1c_H, PMP1u_H, ind_comp),
    by = c("nsim", "n_sample", "d", "c")
  ) %>%
  mutate(
    BESc = prod(PMP1c_h_p1, PMP1c_h_p2, PMP1c_h_p3) / (
      prod(PMP1c_h_p1, PMP1c_h_p2, PMP1c_h_p3) + prod(1 - PMP1c_h_p1, 1 - PMP1c_h_p2, 1 -
                                                        PMP1c_h_p3)
    ),
    BESu = prod(PMP1u_h_p1, PMP1u_h_p2, PMP1u_h_p3) / (
      prod(PMP1u_h_p1, PMP1u_h_p2, PMP1c_h_p3) + prod(1 - PMP1u_h_p1, 1 - PMP1u_h_p2, 1 -
                                                        PMP1u_h_p3)
    )
  )
```

```{r}
rm(Sim_2_Study_1, Sim_2_Study_2, Sim_2_Study_3, Sim_2_Study_4)
```

```{r}
save(Sim_2, file = "../data/Sim_2.RData")
```

```{r}
Sys.time() - t1
```




# Simulation 3 and 4
Define Hypotheses
```{r}
h_p1 <- "mu_1 > mu_2"
h_p2 <- "mu_3 > mu_2"
h_p3 <- "mu_3 > mu_4"

H_correct <- "mu_1 > mu_2 > mu_3 > mu_4" # to compare this, use data from Simulation 2
H <- "mu_1 > mu_3 > mu_2 > mu_4" # in accordance with the partial hypotheses
```

## Simulation 3

### Simulation 3 Study 1: Partial Hypothesis mu_1 > mu_2
```{r}
n_sample <- c(25, 50, 100, 500)
```

Simulates one dataset in which we test H_complete against BES, calculated from the same dataset.
```{r}
Sim_3_Study_1 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      BF_h_p1 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p1
        )
      ),
      BF1u_h_p1 = BF_h_p1$BFtu_confirmatory[[1]],
      PMP1c_h_p1 = BF_h_p1$PHP_confirmatory[[1]],
      PMP1u_h_p1 = BF1u_h_p1 / (BF1u_h_p1 + 1)) %>%
  addIndicator("p1")

```

### Sim_3_Study_2: Partial Hypothesis mu_3 > mu_2
```{r}
Sim_3_Study_2 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      BF_h_p2 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p2
        )
      ),
      BF1u_h_p2 = BF_h_p2$BFtu_confirmatory[[1]],
      PMP1c_h_p2 = BF_h_p2$PHP_confirmatory[[1]],
      PMP1u_h_p2 = BF1u_h_p2 / (BF1u_h_p2 + 1)) %>%
  addIndicator("p2")

```

### Sim_3_Study_3: Partial Hypothesis mu_3 > mu_4
```{r}
Sim_3_Study_3 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      BF_h_p3 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p3
        )
      ),
      BF1u_h_p3 = BF_h_p3$BFtu_confirmatory[[1]],
      PMP1c_h_p3 = BF_h_p3$PHP_confirmatory[[1]],
      PMP1u_h_p3 = BF1u_h_p3 / (BF1u_h_p3 + 1)) %>%
  addIndicator("p3")

```

### Sim_3_Study_4: Aggregate Study 1-3 for complete Dataset
```{r}
# Compute the element-wise mean of s_mu (ensuring a vector output)
pooled_s_mu <- map2(Sim_3_Study_1$s_mu, 
                    map2(Sim_3_Study_2$s_mu, Sim_3_Study_3$s_mu, `+`), 
                    ~ (.x + .y) / 3)

# Compute the element-wise mean of s_Sigma (ensuring a matrix output)
pooled_s_Sigma <- map2(Sim_3_Study_1$s_Sigma, 
                       map2(Sim_3_Study_2$s_Sigma, Sim_3_Study_3$s_Sigma, `+`), 
                       ~ (.x + .y) / 3)

# Create a new DataFrame with the right format
Sim_3 <- Sim_3_Study_1 %>%
  select(nsim, n_sample, d, c, PMP1c_h_p1, PMP1u_h_p1, ind_p1) %>%
  left_join(Sim_3_Study_2 %>% select(nsim, n_sample, d, c, PMP1c_h_p2, PMP1u_h_p2, ind_p2), by = c("nsim", "n_sample", "d", "c")) %>%
  left_join(Sim_3_Study_3 %>% select(nsim, n_sample, d, c, PMP1c_h_p3, PMP1u_h_p3, ind_p3), by = c("nsim", "n_sample", "d", "c"))

# Remove partial DFs, as all information is contained in pooled df
rm(Sim_3_Study_1, Sim_3_Study_2, Sim_3_Study_3) 

Sim_3$s_mu <- pooled_s_mu
Sim_3$s_Sigma <- pooled_s_Sigma

Sim_3 <- Sim_3 %>%
  rowwise() %>%
   mutate(
    BF_H = list(BF(
      x = s_mu,
      Sigma = s_Sigma / (n_sample * 3), # multiply sample size by 3 to pool partial sample sizes
      n = n_sample * 3,
      hypothesis = H
    )),
    BF1u_H = BF_H$BFtu_confirmatory[[1]],
    PMP1c_H = BF_H$PHP_confirmatory[[1]],
    PMP1u_H = BF1u_H / (BF1u_H + 1)
  ) %>%
  addIndicator("comp")

```

### Clean outcome DF and compute BES
```{r}
Sim_3 <- Sim_3 %>%
  select(-c("s_mu", "s_Sigma", "BF_H", "BF1u_H")) %>%
  mutate(
    BESc = prod(PMP1c_h_p1, PMP1c_h_p2, PMP1c_h_p3) / (
      prod(PMP1c_h_p1, PMP1c_h_p2, PMP1c_h_p3) + prod(1 - PMP1c_h_p1, 1 - PMP1c_h_p2, 1 -
                                                        PMP1c_h_p3)
    ),
    BESu = prod(PMP1u_h_p1, PMP1u_h_p2, PMP1u_h_p3) / (
      prod(PMP1u_h_p1, PMP1u_h_p2, PMP1c_h_p3) + prod(1 - PMP1u_h_p1, 1 - PMP1u_h_p2, 1 -
                                                        PMP1u_h_p3)
    )
  )
```

```{r}
save(Sim_3, file = "../data/Sim_3.RData")
```


Timer
```{r}
Sys.time() - t1
```

Clean Workspace
```{r}
rm(Sim_3)
```


## Simulation 4


### Simulation 4 Study 1: Complete Hypothesis
```{r}
n_sample <- c(75, 150, 300, 1500)
```

```{r}
Sim_4_Study_1 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Complete Hypothesis
      BF_H = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = H
        )
      ),
      BF1u_H = BF_H$BFtu_confirmatory[[1]],
      PMP1c_H = BF_H$PHP_confirmatory[[1]],
      PMP1u_H = BF1u_H / (BF1u_H + 1)) %>%
  addIndicator("comp")
```

### Set Saple Size for partial Studies
```{r}
n_sample <- c(25, 50, 100, 500)
```

### Simulation 4 Study 2: mu_1 > mu_2
```{r}
Sim_4_Study_2 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Partial Study 1
      BF_h_p1 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p1
        )
      ),
      BF1u_h_p1 = BF_h_p1$BFtu_confirmatory[[1]],
      PMP1c_h_p1 = BF_h_p1$PHP_confirmatory[[1]],
      PMP1u_h_p1 = BF1u_h_p1 / (BF1u_h_p1 + 1)
    ) %>%
  addIndicator("p1")
```


### Simulation 4 Study 3: mu_3 > mu_2
```{r}
Sim_4_Study_3 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Partial Study 2
      BF_h_p2 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p2
        )
      ),
      BF1u_h_p2 = BF_h_p2$BFtu_confirmatory[[1]],
      PMP1c_h_p2 = BF_h_p2$PHP_confirmatory[[1]],
      PMP1u_h_p2 = BF1u_h_p2 / (BF1u_h_p2 + 1)
    ) %>%
  addIndicator("p2")
```


### Simulation 4 Study 4: mu_3 > mu_4
```{r}
Sim_4_Study_4 <- simulate(nsim = nsim,
                      n_sample = n_sample,
                      d = d,
                      c = c) %>%
    rowwise() %>%
    mutate(
      # BF Partial Study 3
      BF_h_p3 = list(
        BF(
          x = s_mu,
          Sigma = s_Sigma / n_sample,
          n = n_sample,
          hypothesis = h_p3
        )
      ),
      BF1u_h_p3 = BF_h_p3$BFtu_confirmatory[[1]],
      PMP1c_h_p3 = BF_h_p3$PHP_confirmatory[[1]],
      PMP1u_h_p3 = BF1u_h_p3 / (BF1u_h_p3 + 1)
    ) %>%
  addIndicator("p3")
```

### Process Simulation 4
```{r}
# Sample Size to match partial studies
Sim_4_Study_1$n_sample <- Sim_4_Study_1$n_sample/3
```

```{r}
Sim_4 <- Sim_4_Study_2 %>%
  select(nsim, n_sample, d, c, PMP1c_h_p1, PMP1u_h_p1, ind_p1)  %>%
  left_join(
    Sim_4_Study_3 %>% select(nsim, n_sample, d, c, PMP1c_h_p2, PMP1u_h_p2, ind_p2),
    by = c("nsim", "n_sample", "d", "c")
  ) %>%
  left_join(
    Sim_4_Study_4 %>% select(nsim, n_sample, d, c, PMP1c_h_p3, PMP1u_h_p3, ind_p3),
    by = c("nsim", "n_sample", "d", "c")
  ) %>%
  left_join(
    Sim_4_Study_1 %>% select(nsim, n_sample, d, c, PMP1c_H, PMP1u_H, ind_comp),
    by = c("nsim", "n_sample", "d", "c")
  ) %>%
  mutate(
    BESc = prod(PMP1c_h_p1, PMP1c_h_p2, PMP1c_h_p3) / (
      prod(PMP1c_h_p1, PMP1c_h_p2, PMP1c_h_p3) + prod(1 - PMP1c_h_p1, 1 - PMP1c_h_p2, 1 -
                                                        PMP1c_h_p3)
    ),
    BESu = prod(PMP1u_h_p1, PMP1u_h_p2, PMP1u_h_p3) / (
      prod(PMP1u_h_p1, PMP1u_h_p2, PMP1c_h_p3) + prod(1 - PMP1u_h_p1, 1 - PMP1u_h_p2, 1 -
                                                        PMP1u_h_p3)
    )
  )
```

```{r}
rm(Sim_4_Study_1, Sim_4_Study_2, Sim_4_Study_3, Sim_4_Study_4)
```

```{r}
save(Sim_4, file = "../data/Sim_4.RData")
```

```{r}
Sys.time() - t1
```

